\section*{Professional Experience}


\textbf{Backend Developer} \hfill \textit{ABN Amro, Amsterdam}\\
\textit{Jan 2025 – Present}
\begin{itemize}[leftmargin=*]
  \item Responsible for the document folder operations service, one of the core archive services, and supported delivery across four environments from development to production.
  \item Upgraded a single Azure App Service application from Java 17 to Java 25 using OpenRewrite, targeted code cleanup and logic fixes, and Azure release pipeline updates for the new runtime.
  \item Refactored microservices to reduce technical debt and improve service stability by 20\%.
  \item Expanded automated test coverage, contributing to a 25\% reduction in production bugs.
  \item Improved REST API performance by 20\% through logic cleanup and refactoring.
  \item Improved exception handling and logging across backend services to strengthen resilience.
  \item Identified unused document folders in existing records and introduced periodic cleanup logic to reduce storage costs.
  \item Supported Azure certificate lifecycle management for secure internal service communication.
\end{itemize}

\vspace{2pt}
\textbf{Flutter Developer Intern} \hfill \textit{ABN Amro, Amsterdam}\\
\textit{May 2023 – Jul 2023}
\begin{itemize}[leftmargin=*]
  \item Built Flutter app for C4 model visualization and workflow setup.
  \item Prioritized requirements with MoSCoW and maintained client communication.
  \item Presented and delivered the project end to end.
\end{itemize}

\vspace{2pt}
\textbf{Junior Oracle Software Developer} \hfill \textit{Attido SIA, Riga}\\
\textit{Dec 2021 – Aug 2022}
\begin{itemize}[leftmargin=*]
  \item Developed and supported Oracle NetSuite solutions using SuiteScript 2.x and PL/SQL.
  \item Built BI and OCS reports and automated functional tests using Postman and SoapUI.
\end{itemize}